\section{Using Docker}

We have prepared two docker\footnote{\url{https://www.docker.com}} containers,
one for Floodlight and the other for Mininet and Open vSwitch, and a Docker
Compose\footnote{\url{https://docs.docker.com/compose}} configuration. All the
relevant files are under the \code{docker/} directory.

The following versions (or newer) are required:
\begin{itemize}
	\item Docker v17.09.0
	\item Docker Compose v1.17.0
\end{itemize}

From the \code{docker/} folder, Mininet and Floodlight containers can be started
with\footnote{All these commands require root privileges or that the user is in
the \code{docker} group.}:
\begin{verbatim}
$ docker-compose up -d
\end{verbatim}

Docker Compose is just an utility to ease the setup of containers, it is not
strictly necessary to run the containers. Although not recommended, if Compose
is not available, containers can be started using only Docker. The following
\emph{should} be ok (starting from the \code{docker/} directory):
\begin{verbatim}
$ cd mn && docker build -t mininet .
$ cd ../fl && docker build -t floodlight .
$ cd ../../
$ docker network create docker_flmnnet
$ docker volume create docker_fl-m2
$ docker run -p "8080:8080" -p "1044:1044" \
    --rm -v "$(pwd)/:/usr/src/myapp/" \
    -v "docker_fl-m2:/root/.m2" \
    --network docker_flmnnet --name fl floodlight
$ docker run -v "$(pwd)/scripts/:/root/scripts/" \
    -v "/lib/modules:/lib/modules" \
    -v "/tmp/.X11-unix:/tmp/.X11-unix" -e DISPLAY \
    --tty --privileged --link fl --name mn mininet
\end{verbatim}

The first time it is started the Floodlight's container will download all needed
dependencies from the Maven's repository: it may require some time.

To shutdown both containers:
\begin{verbatim}
$ docker-compose down
\end{verbatim}

Or, without Docker Compose:
\begin{verbatim}
docker stop mn
docker stop fl
\end{verbatim}

To view Floodlight's output:
\begin{verbatim}
$ docker logs -f fl
\end{verbatim}

To get a shell inside the Mininet's container:
\begin{verbatim}
$ docker exec -it mn bash
\end{verbatim}
Once inside the Mininet's container, you can find the \code{scripts/} folder
mounted as a volume inside the root's home directory (\code{/root/scripts/}).
Bash scripts to start up Mininet can be ran from here (or just invoke \code{mn}
directly).

To recompile Floodlight, just delete \code{target/floodlight.jar}. Floodlight
will be built again when the container is restarted.

When the Floodlight's container is up, the Floodlight's web UI can be accessed
at:

\begin{center}
	\url{http://127.0.0.1:8080/ui/pages/}
\end{center}

To capture traffic with Wireshark, first enter in the Mininet container and set
the root's password to whatever:
\begin{verbatim}
$ docker exec -it mn bash
# passwd
\end{verbatim}

Then, configure Wireshark to capture through the \code{sshdump} utility. If the
``mn'' hostname does not resolve to the IP address of the container, the address
can be viewed with:
\begin{verbatim}
$ docker inspect mn | grep IPAddress
\end{verbatim}
