\chapter{Tutorial}\label{appendix:tutorial}

The following works with any Linux distribution.

To develop the module, we have forked the Floodlight's repository. The fork is
available on Github at \url{https://github.com/SpeedJack/anaws}. The module is
available on the \code{dualascent} branch (the default branch).

\begin{verbatim}
$ git clone --recurse-submodules \
    https://github.com/SpeedJack/anaws.git
\end{verbatim}

Prerequisites for Floodlight:
\begin{itemize}
	\item JDK 8 (it does not work on more recent versions).
	\item Python with its header files (\code{python-dev}).
	\item Maven (unfortunately, build with \code{ant} is broken due to
		upstream not updating their dependencies' snapshots).
\end{itemize}

We have set up a docker environment to build and run Floodlight and Mininet (see
below). Using the docker containers is recommended, since this is the setup we
have used. Anyway, if docker is not an option, Floodlight can be built with:

\begin{verbatim}
$ mvn package -Dmaven.test.skip=true
\end{verbatim}

To run Floodlight:

\begin{verbatim}
$ ./floodlight.sh
\end{verbatim}

Regarding Mininet and Open vSwitch, we have used the following versions:
\begin{itemize}
	\item Mininet v2.2.2
	\item Open vSwitch 2.13.1
\end{itemize}

Inside the \code{scripts/} folder there are various Bash scripts useful to run
Mininet with various topologies. Other scripts that deserves a mention:
\begin{itemize}
	\item \code{docker/switch-algorithm.sh} that can be used to switch
		between the Dijkstra and the Dual Ascent algorithms in the
		Floodlight's configuration.
	\item \code{docker/set-*.sh} useful to change other configuration
		options of Floodlight by passing the new value as argument.
	\item \code{scripts/collectbw.sh} is the script used to measure the
		host-to-host bandwidth. It is meant to be run from inside
		mininet hosts.
\end{itemize}

\input{tutorial/docker}
